---
title: "Midterm"
author: "Sri Seshadri"
date: "4/15/2018"
output: 
pdf_document:
  toc: true
  toc_depth : 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
library(dplyr)
library(forecast)
library(zoo)
library(ggplot2)
```


# Objective

Predict total sales for every product and store in the next month for the data provided by 1C Company.

# Data

Data was obtained from "https://www.kaggle.com/c/competitive-data-science-predict-future-sales/data"

# Exploratory Data Analysis

```{r}
# Training data set
sales_train <- read.csv("./Midterm/sales_train_v2.csv", header = T, stringsAsFactors = F)
# Item categories
ItemCategories <- read.csv("./Midterm/item_categories.csv")
# Items
Items <- read.csv('./Midterm/items.csv')

# Aggregated data 
Agg_sales_train <- sales_train %>% 
                 dplyr::mutate(date = lubridate::parse_date_time(date,orders = "%d.%m.%Y")) %>% 
                 dplyr::group_by(item_id,shop_id,date_block_num) %>% 
                 dplyr::summarise(MonthlyCts = sum(item_cnt_day),Price = mean(item_price,na.rm = T)) %>% 
                 dplyr::arrange(item_id,shop_id,date_block_num) %>% 
                 dplyr::mutate(Item.Shop = item_id + shop_id / 100) %>% 
                 dplyr::left_join(x = ., y = Items[,2:3])
# Reference frame
df <- data.frame(date_block_num = rep(seq(min(Agg_sales_train$date_block_num),max(Agg_sales_train$date_block_num)),n_distinct(Agg_sales_train$Item.Shop)),
                 Item.Shop = rep(unique(Agg_sales_train$Item.Shop),each = max(Agg_sales_train$date_block_num) - min(Agg_sales_train$date_block_num) + 1)
                 ) %>%
  tidyr::separate(.,2, c("item_id","shop_id"))%>%
        dplyr::mutate(shop_id = ifelse(is.na(shop_id),0,shop_id)) %>% 
        dplyr::mutate(item_id = as.numeric(item_id),shop_id = as.numeric(shop_id))
# Monthly sales reference data frame includes shop id
MonthlySales.ItemShop <- df %>% 
        dplyr::left_join(.,Agg_sales_train[1:5]) %>% 
        dplyr::left_join(.,Items[2:3])

MonthlySales.Train <- MonthlySales.ItemShop %>% 
        dplyr::mutate(ItemShop = item_id + shop_id/100) %>% 
        dplyr::select(date_block_num,ItemShop,MonthlyCts, Price) %>% 
        #dplyr::mutate(MonthlyCts = ifelse(is.na(MonthlyCts),0,MonthlyCts)) %>% 
        dplyr::group_by(ItemShop,date_block_num) %>% 
        dplyr::summarise(Sales = sum(MonthlyCts,na.rm = T)) %>% 
        tidyr::spread(ItemShop,Sales)


# There are several variables that have very little data , what are they
NearZeroVars <- caret::nearZeroVar(MonthlySales.Train, names = F)
MonthlySalests <- as.ts(MonthlySales.Train[,c(1,NearZeroVars)*-1],frequency = 1, start = 0, end = 33)
# Summay by Item Category
MonthlySalebyCategory  <- MonthlySales.ItemShop %>% dplyr::group_by(date_block_num,item_category_id) %>% 
  dplyr::summarise(SaleCounts = sum(MonthlyCts,na.rm = T)) %>% 
  tidyr::spread(item_category_id, SaleCounts)
# How are categories related?

## remove categories that have zero variance
ZeroVars <- caret::nearZeroVar(MonthlySalebyCategory)
cormat <- cor(MonthlySalebyCategory[c(1,ZeroVars)*-1])

RetrieveItemStores <- function(data = MonthlySales.ItemShop, category) {
  data %>% 
    filter(item_category_id %in% category) %>%
    #dplyr::distinct(item_id,shop_id,item_category_id) %>% 
    dplyr::group_by(item_id,shop_id,item_category_id) %>% 
    dplyr::summarise(Datapoints = sum(!is.na(MonthlyCts))/nrow(.)) %>% 
    #dplyr::distinct(item_id,shop_id,keep.all = T) %>% 
    dplyr::ungroup() %>% 
    dplyr::mutate(Item.Shop = item_id + shop_id/100) %>% 
    dplyr::select(Item.Shop,item_category_id,Datapoints) %>% 
    dplyr::filter(Item.Shop %in% as.numeric(colnames(!!MonthlySales.Train)[NearZeroVars*-1])) %>% 
    dplyr::arrange(item_category_id,desc(Datapoints)) %>% 
    dplyr::mutate(item_id = as.integer(floor(Item.Shop)), shop_id = as.integer((Item.Shop - item_id)*100))
}


```

## Data exploration by item category

In this section we'll explore the correlation amongst item categories at a higher level

```{r}
# Correlation plot 
corrplot::corrplot(cormat,order = "hclust",tl.cex = 0.6)
library(reshape2)
HighCors <- subset(melt(cormat,varnames = c('CatA', 'CatB'), value.name = 'Correlations'), Correlations >= 0.8 & Correlations < 1)

HighCors[which(HighCors$CatA == 83),] %>% distinct(CatB)
testdf <- RetrieveItemStores(category = 2) %>% distinct(item_id)


```

## Gaming consoles, accessories and games.

```{r}
MonthlySalebyCategory %>% 
  dplyr::ungroup() %>% 
  dplyr::select(`2`,`19`) %>% ggplot(mapping = aes(x = `19`, y = `2`)) + geom_point() + stat_smooth(method = "lm") + xlab("Games PS3") + ylab("Accesories PS3") + theme_bw()

MonthlySalebyCategory %>% 
  dplyr::ungroup() %>% 
  dplyr::select(`2`,`11`) %>% ggplot(mapping = aes(x = `11`, y = `2`)) + geom_point() + stat_smooth(method = "lm") + xlab("Games Consoles PS3") + ylab("Accesories PS3") + theme_bw()

MonthlySalebyCategory %>% 
  dplyr::ungroup() %>% 
  dplyr::select(`5`,`11`) %>% ggplot(mapping = aes(x = `11`, y = `5`)) + geom_point() + stat_smooth(method = "lm") + xlab("Games Consoles PS3") + ylab("PS Vita") + theme_bw()


```

### Do the linear relationship hold true across shops

The 

```{r}
# Data set up

Categoriesofinterest <- c(2,5,11,19,32,37:40,55:60,62)
Agg_Sales_Category <- Agg_sales_train %>% dplyr::ungroup() %>% 
  dplyr::mutate(shop_id = as.factor(shop_id)) %>% 
  dplyr::filter(item_category_id %in% !!Categoriesofinterest) %>%
  dplyr::group_by(shop_id,item_category_id,date_block_num) %>% 
  dplyr::summarise(Sale = sum(MonthlyCts,na.rm = T)) %>% 
  tidyr::spread(item_category_id,Sale) 

Agg_Price_Category <- Agg_sales_train %>% 
   dplyr::ungroup() %>% 
  dplyr::mutate(shop_id = as.factor(shop_id)) %>% 
  dplyr::filter(item_category_id %in% !!Categoriesofinterest) %>%
  dplyr::group_by(shop_id,item_category_id,date_block_num) %>% 
  dplyr::summarise(Price = mean(Price,na.rm = T)) %>% 
  tidyr::spread(item_category_id,Price)

colnames(Agg_Price_Category)[3:(2+length(Categoriesofinterest))] <- paste0("Price",Categoriesofinterest)
Agg_Sales_Category %<>% dplyr::left_join(.,Agg_Price_Category)
# Plotting 
Agg_Sales_Category %>% ggplot(mapping = aes(x = `19`, y = `2`,col = shop_id)) + geom_point() + stat_smooth(method = "lm",se = F) + xlab("Games PS3") + ylab("Accesories PS3") + theme_bw() + theme(legend.position = "none") + ggtitle( "PS3 Game sales Vs PS3 Accessories", subtitle = "Colored by shop_id")
  
```

# Linear model for PS3 Accesories sale

```{r}
fit.PS3Acc <- lm(`2` ~  `19` + `62` +  Price19 + Price2 + Price62 + shop_id, data = Agg_Sales_Category)
summary(fit.PS3Acc)
broom::augment(fit.PS3Acc) %>% lattice::xyplot(.fitted ~ X2, data = .,xlab = "Accesories PS3 sales", ylab = "Fitted PS3 Accesories sale")

```

## Top Down approach from here?

```{r}
Agg_Sales_Category %>% ggplot(mapping = aes(x = `37`, y = `55`,col = shop_id)) + geom_point() + stat_smooth(method = "lm",se = F) + xlab("Cinema Blue Ray") + ylab("Music CD Local") + theme_bw() + theme(legend.position = "none") + ggtitle( "Cinema Blue Ray Vs Music CD local sales", subtitle = "Colored by shop_id")


```


```{r}
fit <- lm(`55` ~  `37`  +  Price55 + Price37 + shop_id , data = Agg_Sales_Category)
#summary(fit)
broom::augment(fit) %>% lattice::xyplot(.fitted ~ X55, data = .,xlab = "Cinema Blue Ray Sales", ylab = "Fitted Blue Ray sales")
```

# Do the relationships generalize to each item_id?

```{r}
MusicCDtrain <- Agg_sales_train %>% 
  dplyr::ungroup() %>% 
  dplyr::mutate(item__id = as.factor(item_id),shop_id = as.factor(shop_id),Item.Shop = as.factor(Item.Shop)) %>%
  dplyr::mutate(item_category_id = as.factor(item_category_id)) %>% 
  dplyr::filter(item_category_id %in% c(55,37)) %>% 
  dplyr::select(Item.Shop,MonthlyCts,date_block_num) %>% 
  tidyr::spread(Item.Shop,MonthlyCts)
items_id_37 <- RetrieveItemStores(category = 37) %>% distinct(item_id)
items_id_55 <- RetrieveItemStores(category = 55) %>% distinct(item_id)
Predictors <- colnames(MusicCDtrain)[stringr::str_detect(colnames(MusicCDtrain), as.character(items_id_37$item_id))]
Reponses <- colnames(MusicCDtrain)[stringr::str_detect(colnames(MusicCDtrain), as.character(items_id_55$item_id))]


MusicCDtrain %>% dplyr::filter(complete.cases(.))

paste0("`",paste0(Predictors,pad = '`'),collapse = "+")

lm(`1201.04` ~ `935.07`+`965`+`2137.35`+`2631.31`+`3620.31`+`4982.29`+`5331.39`+`5331.42`+`6333.18`+`7265.41`+`7314.07`+`7430.26`+`7485.15`+`7499.45`+`7531.07`+`7651.35`+`8280.44`+`8297.34`+`8318.28`+`8683.31`+`8739.46`+`9165.41`+`9578.29`+`9597.31`+`10021.47`+`10300.48`+`10446.45`+`10876.19`+`11629.21`+`12455.31`+`12459.06`+`12718.57`+`12785.13`+`13785.57`+`13855.57`+`14143.24`+`14271.21`+`14282.22`+`14387.42`+`14522.28`+`14672.33`+`15558.43`+`15702.29`+`16677.29`+`16710.44`+`16725.35`+`16874.26`+`16889.52`+`17174.28`+`17499.57`+`17833.13`+`18259.46`+`18537.13`+`18589.5`+`18592.57`+`18881.38`+`19162.48`+`19185.54`+`19195.35`+`19287.07`+`19547.51`+`21357.49`+`21426.42`+`21542.15`+`21647.5`,data = MusicCDtrain,singular.ok = T)

```

